InspectHistogramsE1

### 2018-03-01 E1/doInferentialStats.Rmd
good

```{r, echo=FALSE, message=FALSE}

gg<-ggplot(estimates, aes(x=stream, y=efficacy)) + geom_point(color="grey") + stat_summary(fun.y="mean",geom="point",size=4, alpha=.5)
show(gg)

library(tidyr)

data.table::dcast(df, orientation~stream,value.var="efficacy")

data.table::dcast(df, stream~orientation,value.var="efficacy")

temp<-estimates[,1:5]
ok<-data.table::dcast(temp, orientation+subject~stream,value.var="efficacy")
#Good except how do you preserve nPassed? Well, nPassed is the same for every factor combintation
data.table::dcast(temp, orientation+subject+nPassed~stream,value.var="efficacy")
#Good so now try with two DVs. 
temp<-estimates[,1:6]
data.table::dcast(temp, orientation+subject+nPassed~stream,
                  value.var=c("efficacy","latency")) #doesn't work
data.table::dcast(temp, orientation+subject+nPassed~stream,value.var="latency")

#The below works but drops many variables, so think about merging later
eff<- data.table::dcast(temp, orientation+subject+nPassed~stream,value.var="efficacy")
lat<-data.table::dcast(estimates, orientation+subject+nPassed~stream,value.var="latency") 
pre<-data.table::dcast(temp, orientation+subject+nPassed~stream,value.var="precision")

#So now scale up to full dataframe

@@

temp<-estimates[1:10,1:5]
temp$nPassed<-NULL
data.table::dcast(temp, subject+orientation~stream,value.var="efficacy")

temp %>%
  gather(key, value, -subject, -orientation, -nPassed, -stream) %>%
  unite(col, key, stream) %>%
  spread(col, value)

data.table::dcast(temp, subject+orientation+nPassed~stream,value.var="efficacy")

foo = data.frame(subject=c("AA","AA","AA","AA","AB","AB","AB","AB"),stream=c("Left","Left","Right","Right","Left","Left","Right","Right"),orientation=c("Canonical","Inverted","Canonical","Inverted","Canonical","Inverted","Canonical","Inverted"),efficacy=c(0.8,0.4,0.5,0.7,0.84,.37,.36,.69))
data.table::dcast(foo, subject+orientation~stream,value.var="efficacy")
foo.short<- foo[,1:4] #,c(2,3,4)]
f<-foo[1:4,2:4]
data.table::dcast(f, orientation~stream,value.var="efficacy")

tempp<-estimates[,4:6]
temppp<- tempp[,c(1,3)]

library(reshape2)

#data.table functions change things in place
require(data.table)
setDT(temp)
data.table::dcast(temp, subject+orientation+X+nPassed~stream,value.var="efficacy")

dcast(foo,group+num_users~times,value.var=c("action_rate","action_rate_c95"))

dcast(temp, subject+nPassed+X+orientation ~stream, value.var=efficacy)
?ddcast(tempp, 
temppp$id<- 1:nrow(temppp)
dcast(temppp, id~stream)
dcast(temppp, efficacy~stream+id)

wide <-  estimates %>%
  tidyr::spread(stream,efficacy)

df$

leftBias<- estimates %>% group_by(subject) %>%

deficitCanonical <- estimates %>% filter( stream=="Left" ) -

Do t tests.

@@

```{r, echo=FALSE, message=FALSE}
#want fig.height of 10 per subject

#Add R parameter estimates to dataframe
df<- merge(df,estimates)

>>>>

```{r, echo=FALSE, message=FALSE}
require(ggplot2)
gg<-ggplot(estimates, aes(x=stream, y=efficacy)) + geom_point(color="grey") + stat_summary(fun.y="mean",geom="point",size=4, alpha=.5)
show(gg)

library(data.table)

#The below works but drops many variables, so think about merging later
eff<- data.table::dcast(estimates, orientation+subject+nPassed~stream,value.var="efficacy")
eff$dv<-"efficacy"
lat<-data.table::dcast(estimates, orientation+subject+nPassed~stream,value.var="latency") 
lat$dv<-"latency"
pre<-data.table::dcast(estimates, orientation+subject+nPassed~stream,value.var="precision") 
pre$dv<-"precision"
all<-rbind(eff,lat,pre)
#I tried to do the above with a single command but makes an error even though StackOverflow example works
#https://stackoverflow.com/questions/37332076/from-long-to-wide-data-with-multiple-columns/37332345
# data.table::dcast(estimates, orientation+subject+nPassed~stream,value.var=c("efficacy","latency"))
head(eff)
```

Calculate bias
```{r , fig.height=40, fig.width=5}
all$leftBias<- all$Left - all$Right
hh<-ggplot(all, aes(x=orientation, y=leftBias)) + facet_grid(dv~.) + geom_point(color="grey") + stat_summary(fun.y="mean",geom="point",size=4, alpha=.5)
hh<-hh+stat_summary(fun.data="mean_cl_boot",geom="errorbar",width=.3,conf.int=.95,
                  width=5,size=1) 
show(hh)
```

Do conventional stats.
```{r}

require(ez)

aa <- ezANOVA(data=filter(all,dv=="efficacy"), dv=leftBias, within=orientation, wid=subject)
cat("F=", aa$ANOVA$F, " p=", aa$ANOVA$p, "\n", sep="")

@@

@@
